---
title: "Plaque psoriasis ML-NMR"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.5cm"
output:
  pdf_document:
  latex_engine: lualatex
fontsize: 11pt
mainfont: Arial
linestretch: 1.5
---
  
```{r, include=FALSE, eval=FALSE, echo=FALSE}
# Secukinumab (司库奇尤单抗, Novartis, IL blocker)
# Etanercept (依那西普, Pfizer, TNFa blocker)
# Ustekinumab (乌司奴单抗, J&J, IL blocker)                       
# Ixekizumab (依克珠单抗, EliLilly, IL blocker)

### 5 AGD
1. In the "FIXTURE" trial, the Secukinu

mab is more effective than Etanercept. (300 mg Secukinumab vs 150 mg Secukinumab vs Placebo vs 50mg etanercept)

2. In the "ERASURE" trial, 300 mg Secukinumab vs 150 mg Secukinumab vs Placebo. 

3. In the "CLEAR" trial, 300 mg Secukinumab vs 150 mg Secukinumab vs Placebo.

4. In the "FEATURE" trial, 300 mg Secukinumab vs 150 mg Secukinumab vs Placebo.

5. In the "JUNCTURE" trial, 300 mg Secukinumab vs 150 mg Secukinumab vs Placebo.

### 4 IPD
1. In the "IXORA" trial, Ixekizumab q2w vs Ustekinumab.

2. In the "UNCOVER-1" trial, 80 mg ixekizumab q2w vs 160 mg ixekizumab q2w vs 80 mg ixekizumab p4w.

3. In the "UNCOVER-2" trial, 80 mg ixekizumab q2w vs 160 mg ixekizumab q2w vs 80 mg ixekizumab p4w vs 50 mg etanercept

4. In the "UNCOVER-3" trial, 80 mg ixekizumab q2w vs 160 mg ixekizumab q2w vs 80 mg ixekizumab p4w vs 50 mg etanercept

5. From the "UNCOVER-2" and "UNCOVER-3", ixekizumab is more effective than Etanercept.

```

## Load the library and set up

```{r, warning=FALSE, message=FALSE, error=FALSE, include=FALSE}

library(multinma)
library(tidyverse)
library(lazyeval)
library(data.table)
library(purrr)
library(kableExtra)
library(rlist) ## save the list as rdata
library(stringr)
library(qdapRegex)
library(gridExtra)
library(lemon)


options(mc.cores = parallel::detectCores())

nc <- switch(tolower(Sys.getenv("_R_CHECK_LIMIT_CORES_")), 
             "true" =, "warn" = 2, 
             parallel::detectCores())
options(mc.cores = nc)

setwd("D:\\MPH-Project")
memory.limit(size=40000) # set memory

```


## Import the saved model result
```{r, warning=FALSE, message=FALSE}

start_time <- Sys.time()
Sys.sleep(5)

# extract the name of model result from folder
temp <- list.files(path='D:\\MPH-Project\\', pattern="*.rdata")

## remove the suffix ".rdata"
temp1 <- lapply(temp, function (x) {
    sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(x))
}) %>%
  as.character()

## get the file path
temp.list <- map(temp, function(x) {paste0("D:\\MPH-Project\\", x)})

FE_net_age_agd.sc1.1 <- list.load(temp.list[[1]])
FE_net_age_agd.sc1.2 <- list.load(temp.list[[2]])
FE_net_age_agd.sc2.1 <- list.load(temp.list[[3]])
FE_net_age_agd.sc2.2 <- list.load(temp.list[[4]])
FE_net_age_agd.sc3.1 <- list.load(temp.list[[5]])
FE_net_age_agd.sc3.2 <- list.load(temp.list[[6]])
FE_net_age_agd.sc4.1 <- list.load(temp.list[[7]])
FE_net_age_agd.sc4.2 <- list.load(temp.list[[8]])

FE_net_age_agd.sc4.3 <- list.load(temp.list[[9]])
FE_net_age_agd.sc4.4 <- list.load(temp.list[[10]])

FE_net_org_df <- list.load(temp.list[[11]])

```

## distribution of the data before and after redistribution

```{r fig.height=10, fig.width=10}
full_ipd <- plaque_psoriasis_ipd %>%
  mutate(   # Check complete cases for covariates of interest
    complete = complete.cases(durnpso, prevsys, bsa, weight, psa, age, male))

#
s.comp <- sum(!full_ipd$complete)
mean.comp <- mean(!full_ipd$complete)

# remove the missing data
full_ipd <- filter(full_ipd, complete)

full_agd <- plaque_psoriasis_agd

## initial count by studyc, age group, pasi75 group
full.crs <- full_ipd %>%
  mutate(sub_age = ifelse(age>=47, "gt or eq 47", "lt 47"),
         cat_pas = ifelse(pasi75 == 1, "yes", "no")) %>%
  count(studyc, trtc, cat_pas, sub_age)

## histogram by studyc, trtc before redistribution
ggplot(full.crs) +
  geom_bar(aes(x=sub_age, y=n, fill = cat_pas), stat = "identity") +
  facet_wrap(vars(studyc, trtc)) +
  labs(title = "Distribution before simulation by trials, studies")+
  guides(fill=guide_legend(title="PASI75")) +
  xlab("Age group") +
  ylab("Frequency") + 
  theme_multinma()

## nest data
full_ipd.muta <- full_ipd %>%
  group_by(studyc) %>%
  nest()

## create model and then predict the f(pasi75)
set.seed(1234)

full_ipd.muta$data <- map(full_ipd.muta$data, function(df){
  a <- glm(pasi75 ~ age*trtc + bmi*trtc + male*trtc + bsa*trtc + weight*trtc + durnpso*trtc, family = "binomial", data = df, na.action = "na.exclude")
  df %>%
    mutate(lp = predict(a, type = "link"))
})

# Ensures reproducible
full_ipd.muta$data <- map(full_ipd.muta$data, function(df){
  df %>%
    mutate(lp2 = if_else(age < 47 & trtc %in% c("PBO"),  lp - 0.2, lp),
           lp2 = if_else(age < 47 & !trtc %in% c("PBO"), lp2 + 0.2, lp2),
           risk = plogis(lp2),
           ## Next line is stochastic
           pasi75_sim = rbinom(n = length(lp2), size = 1, prob = risk))
})

full_ipd <- full_ipd.muta %>%
  unnest(data) %>%
  filter(!is.na(pasi75_sim))  ## 6 records with missing PASI75 deleted from data

full.crs2 <- full_ipd %>%
  mutate(cat_pas = ifelse(pasi75_sim == 1, "yes", "no"),
         sub_age = ifelse(age>=47, "gt or eq 47", "lt 47")) %>%
  count(studyc, trtc, cat_pas, sub_age)

## histogram by studyc, trtc after redistribution
ggplot(full.crs2) +
  geom_bar(aes(x=sub_age, y=n, fill = cat_pas), stat = "identity") +
  facet_wrap(vars(studyc, trtc)) +
  labs(title = "Distribution after simulation by trials, studies") +
  guides(fill=guide_legend(title="PASI75")) +
  theme_multinma()


```
When we compare two plots, we could find the percentage of PASI75=Yes in the younger population would be higher than the elder.

# density of continous covariates

```{r distribution_of_covariates, fig.width=8, fig.height=8, out.width="100%"}
#####################################################################
##                          Data preparation                       ##
#####################################################################

## Data transformation in IPD
sub_ipd <- full_ipd %>% 
  mutate(# Variable transformations
    bsa = bsa / 100,
    prevsys = as.numeric(prevsys),
    psa = as.numeric(psa),
    weight = weight / 10,
    durnpso = durnpso / 10,
    # Treatment classes
    trtclass = case_when(trtn == 1 ~ "Placebo",
                         trtn %in% c(2, 3, 5, 6, 7) ~ "IL blocker",
                         trtn == 4 ~ "TNFa blocker"),
    sub_age = ifelse(age>=47, "gt or eq 47", "lt 47"),
    sub_sex = ifelse(male == "TRUE", "male", "female"),
    male = ifelse(male == "TRUE", 1, 0))

## subgroup result generated from IPD
## five covariate durnpso, prevsys, bsa, weight, psa, (age/male)
## include studyc, trt, trtclass, trtn, trtc_long into by vars

sub_eff_func <- function(group_vars, name_) {
  
  sub_ipd %>% 
    group_by(!!!group_vars) %>%
    summarise(age_mean = mean(age),
              age_sd = sd(age),
              bmi_mean = mean(bmi, na.rm = TRUE),
              bmi_sd = sd(bmi, na.rm = TRUE),
              weight_mean = mean(bmi, na.rm = TRUE),
              weight_sd = sd(bmi, na.rm = TRUE),
              durnpso_mean = mean(durnpso),
              durnpso_sd = sd(durnpso),
              pasi75_n = n(),
              pasi75_r = sum(pasi75),
              pasi90_n = n(),
              pasi90_r = sum(pasi90),
              pasi100_n = n(),
              pasi100_r = sum(pasi100), 
              psa = mean(psa), 
              prevsys = mean(prevsys), 
              male = mean(male),
              bsa_mean = mean(bsa), 
              bsa_sd = sd(bsa)) %>%
    mutate(studyc = paste(studyc, name_)) 
  
}

## convert IPD to AgD
ipd_agd <- sub_eff_func(quos(studyc, trtc, trtclass, trtn, trtc_long), "IPD")

## aggregrate data age-specific subgroup
agd_sub_age <- sub_eff_func(quos(studyc, trtc, trtclass, trtn, trtc_long, sub_age), "SUB")

## aggregrate data sex-specific subgroup
agd_sub_sex <- sub_eff_func(quos(studyc, trtc, trtclass, trtn, trtc_long, sub_sex), "SUB")

## aggregrate data factorial combination of age and sex subgroup
agd_sub_agesex <- sub_eff_func(quos(studyc, trtc, trtclass, trtn, trtc_long, sub_age, sub_sex), "SUB")


## original AgD mutation
sub_agd <- full_agd %>% 
  mutate(
    # Variable transformations
    bsa_mean = bsa_mean / 100,
    bsa_sd = bsa_sd / 100,
    prevsys = prevsys / 100,
    psa = psa / 100,
    male = male / 100,
    weight_mean = weight_mean / 10,
    weight_sd = weight_sd / 10,
    durnpso_mean = durnpso_mean / 10,
    durnpso_sd = durnpso_sd / 10,
    
    # Treatment classes
    trtclass = case_when(trtn == 1 ~ "Placebo",
                         trtn %in% c(2, 3, 5, 6, 7) ~ "IL blocker",
                         trtn == 4 ~ "TNFa blocker")
  )



## combine AGD with study level/treatment level subgroup
sub_agd1 <- bind_rows(sub_agd,
                      agd_sub_age, 
                      ipd_agd)

# Get mean and sd of covariates in each study
ipd_summary <- sub_ipd %>% 
  group_by(studyc) %>% 
  summarise_at(vars(weight, durnpso, bsa, age), list(mean = mean, sd = sd, min = min, max = max)) %>% 
  pivot_longer(weight_mean:age_max, names_sep = "_", names_to = c("covariate", ".value")) %>% 
  # Assign distributions
  mutate(dist = recode(covariate,
                       bsa = "dlogitnorm",
                       durnpso = "dgamma",
                       weight = "dgamma",
                       age = "dgamma")) %>% 
  # Compute density curves
  group_by(studyc, covariate) %>% 
  mutate(value = if_else(dist == "dlogitnorm",
                         list(seq(0, 1, length.out = 101)),
                         list(seq(min*0.8, max*1.2, length.out = 101)))) %>% 
  unnest(cols = value) %>% 
  mutate(dens = eval(call(first(dist), x = value, mean = first(mean), sd = first(sd))))

# Plot histograms and assumed densities
sub_ipd %>% 
  pivot_longer(c(weight, durnpso, bsa, age), names_to = "covariate", values_to = "value") %>% 
  ggplot(aes(x = value)) +
  geom_histogram(aes(y = stat(density)), 
                 binwidth = function(x) diff(range(x)) /nclass.Sturges(x),
                 boundary = 0,
                 fill = "grey50") +
  geom_line(aes(y = dens), data = ipd_summary,
            colour = "darkred", size = 0.5) +
  facet_wrap(~studyc + covariate, scales = "free", ncol = 3) +
  theme_multinma()

```

## Original scenario vs 3 IPD + 1 agg IPD + 5 agd vs 3 IPD + 1 sub IPD + 5 agd
## Model comparison under different scenarios

Then in the age subgroup results, we would compare the result of original scenario, scenario 1, and scenario 2 with age-specific subgroup effects.

```{r, warning=FALSE, message=FALSE}

## combine coefficients of model in one list
re.list <- list(FE_net_org_df, FE_net_age_agd.sc1.1, FE_net_age_agd.sc1.2, FE_net_age_agd.sc2.1, FE_net_age_agd.sc2.2, FE_net_age_agd.sc3.1, FE_net_age_agd.sc3.2, FE_net_age_agd.sc4.1, FE_net_age_agd.sc4.2)

extrac.list <- function (list.new) {
listof.coeff <- list()
listof.dic <- list()
listof.resd <- list()
listof.pd <- list()
listof.releff <- list()


for (i in 1:length(list.new)) {
  
  ## coefficient
  dt.out <- summary(list.new[[i]], "d", "beta", "mu") %>%
  as_tibble() %>% 
  select(parameter, mean, sd, `2.5%`, `97.5%`) %>%
  # mutate_if(is.numeric, round, digits = 2) %>%
  rename(lower = `2.5%`, upper = `97.5%`) %>%
  mutate(id = i)

  ## model fit
  mf.out <- dic(list.new[[i]])
  
  dic <- mf.out[["dic"]]
  pd <-  mf.out[["pd"]]
  resd <-  mf.out[["resdev"]]
  ## relative treatment
  # rt_fig <- as.data.frame(relative_effects(list.new[[i]]))
  rt_fig <- relative_effects(list.new[[i]])[["summary"]]
 
  listof.coeff[[i]] <- dt.out
  listof.dic[[i]] <- dic
  listof.pd[[i]] <- pd
  listof.resd[[i]] <- resd
  listof.releff[[i]] <- rt_fig

}

  comb.list <- list(listof.coeff, listof.dic, listof.pd, listof.resd, listof.releff)
  return(comb.list)
}

comb.list.age <- extrac.list(re.list)

```

### Tables of model results
```{r, message=FALSE, warning=FALSE}

## set the coefficients together
coeff.mod1.f <- do.call("bind_rows", comb.list.age[[1]]) %>%
  mutate(scenario = case_when(id %in% 1 ~ "ipd + agd", 
                              id %in% c(2,4,6,8) ~ "ipd + agg ipd + agd",
                              id %in% c(3,5,7,9) ~ "ipd + sub ipd + agd")) %>%
  group_by(parameter, scenario) %>%
  summarise_at(c("mean", "lower", "upper"), mean) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  mutate("Mean (95% CI)" = paste0(mean, " (", lower, ", ", upper, ")"))

## set the coefficients together for tables
coeff.mod1.t <- coeff.mod1.f %>%
mutate("Mean (95% CI)" = paste0(mean, " (", lower, ", ", upper, ")")) %>%
pivot_wider(id_cols = parameter, names_from = scenario, names_sep = " ", values_from = c(`Mean (95% CI)`)) %>%
  filter(!is.na(`ipd + agd`))

#####################################################################
##     Overall Model information under different scenarios         ##
#####################################################################

kbl(coeff.mod1.t %>% filter(grepl('mu', parameter)) %>% mutate(parameter = substring(parameter, 4, nchar(parameter)-1)), booktabs = T, align = "c",
    caption = "The comparisons of intercept between different scenarios", 
    col.names = c("Intercepts", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD", 
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

## coefficients of model
kbl(coeff.mod1.t %>% filter(grepl('beta', parameter)) %>% mutate(parameter = substring(parameter, 6, nchar(parameter)-1)), booktabs = T, align = "c",
    caption = "The comparisons between different scenarios", 
    col.names = c("Coefficients", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD", 
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

## treatment difference compared to Placebo
kbl(coeff.mod1.t %>% filter(grepl('^d', parameter)) %>% mutate(parameter = substring(parameter, 3, nchar(parameter)-1)), booktabs = T, align = "c",
    caption = "The comparisons of treatment effects between different scenarios", 
    col.names = c("treatment effects", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD", 
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

```


## Forest plot of model results
```{r fig.height=12, fig.width=12}
## forest plot to combine results of different scenarios
coeff.mod.f <- coeff.mod1.f  %>%
  mutate(parameter = ifelse(grepl('mu', parameter), 
                           substring(parameter, 4, nchar(parameter)-1), 
                    ifelse(grepl('beta', parameter), 
                           substring(parameter, 6, nchar(parameter)-1), 
                           substring(parameter, 3, nchar(parameter)-1)))) %>%
  arrange(parameter, scenario)

coe.forest.fig <- function(filter_1, x1, y1, x2, ypot, dt=coeff.mod.f, rfl=0) {
ggplot(dt %>% filter(grepl(filter_1, parameter)), aes(x = mean, y = parameter, color = factor(scenario))) +
    geom_point(position = position_dodge(width = ypot)) +
  geom_errorbarh(aes(xmax = upper, xmin = lower), height=.1, position = position_dodge(width = ypot)) +
  geom_vline(xintercept=rfl, color="black", linetype="dashed", alpha=.5) +
  geom_text(aes(x = x2, label = `Mean (95% CI)`), position = position_dodge(width = ypot)) +
  scale_x_continuous(limits = c(x1, y1)) +
  ylab(" ") +
  theme(legend.title = element_blank())
}

## age and interaction
p1 <- coe.forest.fig("age", -0.55, 0.2, -0.4, 0.4)

## weight and interaction
p2 <- coe.forest.fig("weight", -0.7, 0.2, -0.5, 0.4)

## psa and interaction
p3 <- coe.forest.fig("psa", -2, 1, -1.5, 0.4)

## prevsys and interaction
p4 <- coe.forest.fig("prevsys", -1.9, 1, -1.4, 0.4)

## durnpso and interaction
p5 <- coe.forest.fig("durnpso", -0.6, 0.3, -0.4, 0.4)

## bsa and interaction
p6 <- coe.forest.fig("bsa", -8, 4, -6, 0.4)

grid_arrange_shared_legend(p1, p2, p3, p4, p5, p6, ncol=2, nrow=3, position='bottom', top = grid::textGrob('Forest plot of model coefficients'))

```

```{r fig.height=8, fig.width=8}

coe.forest.fig("^d", -2, 5, -1, 0.4, coeff.mod1.f, 1) +
  labs(title = "Forest plot of treatment effects compared to placebo\nunder different scenarios") +
  xlab(" ")

```

## Relative effects under different scenarios

```{r fig.height=8, fig.width=8, message=FALSE, out.width="100%"}

reff.list <- list(comb.list.age[[5]][[1]], comb.list.age[[5]][[2]], comb.list.age[[5]][[3]],
                  comb.list.age[[5]][[4]], comb.list.age[[5]][[5]],
                  comb.list.age[[5]][[6]], comb.list.age[[5]][[7]],
                  comb.list.age[[5]][[8]], comb.list.age[[5]][[9]])

# draw the figures of relative effects
releff.dt <- rbindlist(reff.list, idcol="id") %>%
  mutate(scenario = case_when(id %in% 1 ~ "ipd + agd", 
                              id %in% c(2,4,6,8) ~ "ipd + agg ipd + agd",
                              id %in% c(3,5,7,9) ~ "ipd + sub ipd + agd")) %>%
# , par = trimws(word(word(parameter, 2, sep=":"), 1, sep="]"))) 
  group_by(parameter, scenario) %>%
  summarise_at(c("mean", "2.5%", "97.5%"), mean) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  mutate("Mean (95% CI)" = paste0(mean, " (", `2.5%`, ", ", `97.5%`, ")")) %>%
  pivot_wider(id_cols = parameter, names_from = scenario, names_sep = " ", values_from = c(`Mean (95% CI)`)) %>%
  filter(!is.na(`ipd + agd`))
  
  # mutate(parameter = substring(parameter, 3, nchar(parameter)-1))

releff.dt$r.numb <- seq.int(nrow(releff.dt))

## generate long table
kbl(releff.dt %>% filter(r.numb < 37) %>% select(-r.numb), booktabs = T, align = "c",
    caption = "The comparisons of relative treatment effects between different scenarios", 
    col.names = c("Relative Effects", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD", 
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

kbl(releff.dt %>% filter(r.numb >= 37) %>% select(-r.numb), booktabs = T, align = "c",
    caption = "The comparisons of relative treatment effects between different scenarios (continued)",
    col.names = c("Relative Effects", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD",
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header"), full_width = T)

```

## Original scenario vs 1 IPD + 3 agg IPD + 5 agd vs 1 IPD + 3 sub IPD + 5 agd

```{r, warning=FALSE, message=FALSE}

## combine coefficients of model in one list
re.list.2 <- list(FE_net_org_df, FE_net_age_agd.sc4.3, FE_net_age_agd.sc4.4)

extrac.list <- function (list.new) {
listof.coeff <- list()
listof.dic <- list()
listof.resd <- list()
listof.pd <- list()
listof.releff <- list()


for (i in 1:length(list.new)) {
  
  ## coefficient
  dt.out <- summary(list.new[[i]], pars= c("d", "beta", "mu")) %>%
  as_tibble() %>% 
  select(parameter, mean, sd, `2.5%`, `97.5%`) %>%
  # mutate_if(is.numeric, round, digits = 2) %>%
  rename(lower = `2.5%`, upper = `97.5%`) %>%
  mutate(id = i)

  ## model fit
  mf.out <- dic(list.new[[i]])
  
  dic <- mf.out[["dic"]]
  pd <-  mf.out[["pd"]]
  resd <-  mf.out[["resdev"]]
  ## relative treatment
  # rt_fig <- as.data.frame(relative_effects(list.new[[i]]))
  rt_fig <- relative_effects(list.new[[i]])[["summary"]]
 
  listof.coeff[[i]] <- dt.out
  listof.dic[[i]] <- dic
  listof.pd[[i]] <- pd
  listof.resd[[i]] <- resd
  listof.releff[[i]] <- rt_fig

}

  comb.list <- list(listof.coeff, listof.dic, listof.pd, listof.resd, listof.releff)
  return(comb.list)
}

comb.list.age.2 <- extrac.list(re.list.2)

```

### Tables of model results
```{r, message=FALSE, warning=FALSE}

## set the coefficients together
coeff.mod1.f.2 <- do.call("bind_rows", comb.list.age.2[[1]]) %>%
  mutate(scenario = case_when(id %in% 1 ~ "ipd + agd", 
                              id %in% c(2) ~ "ipd + agg ipd + agd",
                              id %in% c(3) ~ "ipd + sub ipd + agd")) %>%
  mutate_if(is.numeric, round, digits = 3) %>%
  mutate("Mean (95% CI)" = paste0(mean, "(", lower, ", ", upper, ")"))

## set the coefficients together for tables
coeff.mod1.t.2 <- coeff.mod1.f.2 %>%
mutate("Mean (95% CI)" = paste0(mean, "(", lower, ", ", upper, ")")) %>%
pivot_wider(id_cols = parameter, names_from = scenario, names_sep = "_", values_from = c(`Mean (95% CI)`)) %>%
  filter(!is.na(`ipd + agd`) & !is.na(`ipd + agg ipd + agd`) & !is.na(`ipd + sub ipd + agd`))

#####################################################################
##     Overall Model information under different scenarios         ##
#####################################################################

kbl(coeff.mod1.t.2 %>% filter(grepl('mu', parameter)) %>% mutate(parameter = substring(parameter, 4, nchar(parameter)-1)), booktabs = T, align = "c",
    caption = "The comparisons of intercept between different scenarios", 
    col.names = c("Intercepts", "4 IPD + 5 AgD", "1 IPD + 3 aggregated IPD + 5 AgD", 
                     "1 IPD + 3 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

## coefficients of model
kbl(coeff.mod1.t.2 %>% filter(grepl('beta', parameter)) %>% mutate(parameter = substring(parameter, 6, nchar(parameter)-1)), booktabs = T, align = "c",
    caption = "The comparisons between different scenarios", 
    col.names = c("Coefficients", "4 IPD + 5 AgD", "1 IPD + 3 aggregated IPD + 5 AgD", 
                     "1 IPD + 3 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

## treatment difference compared to Placebo
kbl(coeff.mod1.t.2 %>% filter(grepl('^d', parameter)) %>% mutate(parameter = substring(parameter, 3, nchar(parameter)-1)), booktabs = T, align = "c",
    caption = "The comparisons of treatment effects between different scenarios", 
    col.names = c("treatment effects", "4 IPD + 5 AgD", "1 IPD + 3 aggregated IPD + 5 AgD", 
                     "1 IPD + 3 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)
```

```{r fig.height=8, fig.width=8}

coe.forest.fig("^d", -2, 5, -1, 0.4, coeff.mod1.f.2, 1) +
  labs(title = "Forest plot of treatment effects compared to placebo\nunder different scenarios") +
  xlab(" ")

```


## Forest plot of model results
```{r fig.height=14, fig.width=14}
## forest plot to combine results of different scenarios
coeff.mod.f.2 <- coeff.mod1.f.2  %>%
  mutate(parameter = ifelse(grepl('mu', parameter), 
                           substring(parameter, 4, nchar(parameter)-1), 
                    ifelse(grepl('beta', parameter), 
                           substring(parameter, 6, nchar(parameter)-1), 
                           substring(parameter, 3, nchar(parameter)-1)))) %>%
  arrange(parameter, scenario)

## age and interaction
p1 <- coe.forest.fig("age", -0.55, 0.2, -0.4, 0.4, coeff.mod.f.2)

## weight and interaction
p2 <- coe.forest.fig("weight", -0.7, 0.2, -0.5, 0.4, coeff.mod.f.2)

## psa and interaction
p3 <- coe.forest.fig("psa", -3, 1.5, -2, 0.4, coeff.mod.f.2)

## prevsys and interaction
p4 <- coe.forest.fig("prevsys", -3, 1, -2, 0.4, coeff.mod.f.2)

## durnpso and interaction
p5 <- coe.forest.fig("durnpso", -0.8, 0.5, -0.6, 0.4, coeff.mod.f.2)

## bsa and interaction
p6 <- coe.forest.fig("bsa", -11, 7, -9, 0.4, coeff.mod.f.2)


grid_arrange_shared_legend(p1, p2, p3, p4, p5, p6, ncol=2, nrow=3, position='bottom', top = grid::textGrob('Forest plot of model coefficients'))

```

## Relative effects under different scenarios

```{r fig.height=8, fig.width=8, message=FALSE, out.width="100%"}

reff.list.2 <- list(comb.list.age.2[[5]][[1]], comb.list.age.2[[5]][[2]], comb.list.age.2[[5]][[3]])

# draw the figures of relative effects
releff.dt.2 <- rbindlist(reff.list.2, idcol="id") %>%
  mutate(scenario = case_when(id %in% 1 ~ "ipd + agd", 
                              id %in% c(2) ~ "ipd + agg ipd + agd",
                              id %in% c(3) ~ "ipd + sub ipd + agd")) %>%
         # ,par = trimws(word(word(parameter, 2, sep=":"), 1, sep="]"))) 
  mutate_if(is.numeric, round, digits = 3) %>%
  mutate("Mean (95% CI)" = paste0(mean, " (", `2.5%`, ", ", `97.5%`, ")")) %>%
  pivot_wider(id_cols = parameter, names_from = scenario, names_sep = " ", values_from = c(`Mean (95% CI)`)) %>%
  filter(!is.na(`ipd + agd`))
  # mutate(parameter = substring(parameter, 3, nchar(parameter)-1))

releff.dt.2$r.numb <- seq.int(nrow(releff.dt.2))

## generate long table
kbl(releff.dt.2 %>% filter(r.numb < 37) %>% select(-r.numb), booktabs = T, align = "c",
    caption = "The comparisons of relative treatment effects between different scenarios", 
    col.names = c("Relative Effects", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD", 
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), full_width = T)

kbl(releff.dt.2 %>% filter(r.numb >= 37) %>% select(-r.numb), booktabs = T, align = "c",
    caption = "The comparisons of relative treatment effects between different scenarios (continued)",
    col.names = c("Relative Effects", "4 IPD + 5 AgD", "3 IPD + 1 aggregated IPD + 5 AgD",
                     "3 IPD + 1 sub-grouped IPD + 5 AgD")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header"), full_width = T)

```

```{r}
end_time <- Sys.time()

## calculate the running time
start_time-end_time

## pop up notification when it's DONE!
system('CMD /C "ECHO The R process has finished running && PAUSE"',
       invisible=FALSE, wait=FALSE)

```
















